Appendix

### 2019-11-27 manuscript/appendix.Rmd
brute force explore hu variation

>>>>

```{r eval = FALSE}
# brute force check random slopes
# dt <- readRDS("data/dt.rds")
dt <- readRDS("data/dt_scaled.rds")

ggplot(data = dt) +
  geom_point(aes(x = forest, y = tp, color = hu4_zoneid))

res <- list()
for(i in unique(dt$hu4_zoneid)){
  dt_sub <- dplyr::filter(dt, hu4_zoneid == i)
  print(i)
  print(nrow(dt_sub))
  if(nrow(dt_sub) > 4){
  res[[i]] <- data.frame(
    n = nrow(dt_sub), 
  estimate = broom::tidy(cor.test(
    dt_sub$forest, dt_sub$tp
    ))$estimate, 
  stringsAsFactors = FALSE)
  }else{
    res[[i]] <- data.frame(n = NA, 
                           estimate = NA,
                           stringsAsFactors = FALSE)
  }
}

res <- dplyr::bind_rows(res)
res <- dplyr::filter(res, !is.na(n))

ggplot(data = res, aes(x = estimate, y = 1, color = n)) +
  geom_point()
```
